---
title: "20181204_140712_Final"
author: "Alison E. Turnbull"
date: "December 4, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("tidyverse")
```

### Motivation and Overview: Provide an overview of the project goals and the motivation for it. Consider that this will be read by people who did not see your project proposal.

### Related Work: Anything that inspired you, such as a paper, a web site, or something we discussed in class.

### Initial Questions: What questions are you trying to answer? How did these questions evolve over the course of the project? What new questions did you consider in the course of your analysis?

### Data: What is the data source? Document the data import, wrangling, etc.

##### These data were collected as part of an IRB-approved randomized train of an intervention designed 



##### Because there are potential identifiers in the data, I am going to create a de-identified version for this analysis.  This next chunk cannot be evaluated, but it will show you where the data frame containing data on the physicians who participated in the study came from and was wrangled.  I will then remove these original data frames, leaving behind only the di-identified version for the rest of this analysis. 
```{r, warning=FALSE, message=FALSE, eval=FALSE}
## Loading in the study data which is contained in multiple dataframes connected by a shared unique identifier variable called "uid"
    load("X:/Moore Early Career Investigator Award/Aim 3/Study Data/Data shared with Di Chen/[20180312] dataset v5/20180313_SCIP data & codebook.RData")

## Loading data on location of home hospital and merging that information into the dataframe containing physician characteristics
    location<-read_csv("20180704_Participant hospital locations.csv")
    md<-merge(md, location, by="uid")

## Extracting variables relevant to this analysis    
 ## The md dataframe contains physician characteristics
    md<-md %>%
        select(uid, age, gender, race, tx, religion_importance, icu_weeks, icu_type, train_med, train_sx, train_em, train_anes, hosp_ac_st_univ, baltimore, state)
    
 ## The pre_dta dataframe contains data the doctors self-reported before the simulation
    pre_dta<-pre_dta %>%
        select(uid, prognosis_survive, prognosis_mc, consult_palliative)
    
 #The post_dta dataframe contains data the doctors self-reported after the simulation       
    post_dta<-post_dta %>%
        select(uid, disagreement_perceived, tracheotomy, withdraw_life_support)
    
 #The post_sp dataframe contains actor assessments of the simulation reported immediately afterward
    post_sp<-post_sp %>%
        select(uid, effort_to_help, effort_to_listen, effort_to_include, disagreement, sp)
    
 #The outcome dataframe contains assessments of the simulations provided by blinded colleague reviewers reading transcriptions
    outcome<-outcome %>%
        filter(assesser=="final") %>%
        select(uid, comfort, comfort_understandable, withdraw, death, death_word, prognosis, assesser)
    
## Merging all these data sources together     
    dta<-Reduce(function(x, y) merge(x, y, by="uid"), list(md, pre_dta, post_dta, post_sp, outcome))
    
 ## Removing redundant dataframes and those with potentially identifying information
    rm(key, location, md, outcome, post_dta, post_sp, pre_dta)
     
    write_csv(dta, "140.712_Final_dta.csv") 
```

##### Reading in sharable csv files  
```{r, warning=FALSE, message=FALSE}
    dta<-read_csv("140.712_Final_dta.csv")
    sum_measures<-read_csv("summary_measures.csv")
        ## Renaming the unique identifier in this dataframe for merging purposes:
        sum_measures<-rename(sum_measures, uid=study_id)
    
    ## Here's data on how long each simulation went on.
    duration<-read_csv("20180810_Simulation_duration.csv")
    sum_measures<-merge(sum_measures, duration, by="uid")
```

##### Cleaning the summary measures and creating new variables
```{r}
sum_measures<-sum_measures %>%
    mutate(mins=signif(as.numeric(duration/60)), 3) %>%          ## Total duration of the simulation in minutes
    mutate(wrd_total=wrd_cnt_phys+wrd_cnt_prox) %>%              ## Total number of words spoken during simulation
    
    mutate(totalwrd_per_min=wrd_total/mins) %>%                  ## Total words per minute within simulation
    mutate(physwrd_per_min=wrd_cnt_phys/mins) %>%                ## Physician words per minute
    mutate(proxwrd_per_min=wrd_cnt_prox/mins) %>%                ## Proxy words per minute
    mutate(wrdratio_physprox=wrd_cnt_phys/wrd_cnt_prox) %>%      ## Ratio of physician:proxy words
    
    mutate(uttratio_physprox=uttr_cnt_phys/uttr_cnt_prox) %>%    ## Ratio of physician:proxy utterances
    
    mutate(i_my_cnt=pron_i_cnt+pron_my_cnt) %>%                  ## Count of the number of the pronouns "I" and "my"
    mutate(you_your_cnt=pron_you_cnt+pron_your_cnt) %>%          ## Count of the number of the pronouns "you" and "your"
    mutate(she_hers=pron_she_cnt+pron_her_cnt+pron_hers_cnt) %>% ## Count of the number of the pronouns "she" and "her" and "hers"
    mutate(he_his=pron_he_cnt+pron_his_cnt) %>%                  ## Count of the number of the pronouns "he" and "his"
    mutate(i_my_prop=signif(i_my_cnt/wrd_total, 3)) %>%          ## Proportion of all words that are "I" or "my"
    mutate(you_your_prop=signif(you_your_cnt/wrd_total, 3)) %>%  ## Proportion of all words that are "you" or "yours"
    mutate(she_her_prop=signif(she_hers/wrd_total, 3)) %>%       ## Proportion of all words that are "her" or "hers"
    mutate(he_his_prop=signif(he_his/wrd_total, 3))  %>%         ## Proportion of all words that are "he" or "his"
    
    mutate(phys_verb_prop=signif(phys_verb_cnt/wrd_cnt_phys, 3)) %>%     ## Proportion of physician words that are verbs
    mutate(phys_noun_prop=signif(phys_noun_cnt/wrd_cnt_phys, 3)) %>%     ## Proportion of physician words that are verbs
    mutate(phys_adj_prop=signif(phys_adjective_cnt/wrd_cnt_phys, 3)) %>% ## Proportion of physician words that are verbs
    mutate(phys_adv_prop=signif(phys_adverb_cnt/wrd_cnt_phys, 3))%>%     ## Proportion of physician words that are verbs
    
    mutate(voa_prop=signif(voa_cnt/wrd_total, 3)) %>%                    ## Proportion of words in the VOA lexicon
    mutate(nlm_prop=signif(nlm_minus_voa_cnt/wrd_total, 3))              ## Proportion of words in the nlm but not not VOA lexicon
    
    
    ## Keeping the cleaned features
    sum_measures<-sum_measures %>%
        select(uid, wrd_total, wrd_cnt_phys, wrd_cnt_prox, wrdratio_physprox, mins, totalwrd_per_min, 
              physwrd_per_min, proxwrd_per_min, uttratio_physprox, mean_wrds_uttr_phys, median_wrds_uttr_phys, 
              mean_wrds_uttr_prox, median_wrds_uttr_prox,
              voa_prop, nlm_prop, fk_score, gf_score, pattern_sent,
              wwbp_to_past, wwbp_to_present, wwbp_to_future,
              i_my_prop, you_your_prop, she_her_prop, he_his_prop, 
              phys_verb_prop, phys_noun_prop, phys_adj_prop, phys_adv_prop)
```


*Exploratory Data Analysis: What visualizations did you use to look at your data in different ways? What are the different statistical methods you considered? Justify the decisions you made, and show any major changes to your ideas. How did you reach these conclusions? You should use this section to motivate the statistical analyses that you decided to use in the next section.

*Data Analysis: What statistical or computational method did you apply and why? What others did you consider?

*Narrative and Summary: What did you learn about the data? How did you answer the questions? How can you justify your answers? What are the limitations of the analyses?
